---
title: "Labor Flows Results"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      error = FALSE)

```


```{r parameters, include = FALSE}

# ## Set parameters
# base_path = "C:/Users/zachm/Documents/George Mason/Projects/Labor Flows Paper/Results"
# 
# ## Docked results path
# docked_path = "3_1_Homogenous_Labor/3_1_2_labor_demand_shock"
# 
# ## WFH comparison path
# wfh_path = "3_1_WFH_extension/3_1_2_labor_demand_shock/Case_1"
# 
# 
# ## Where should the results be written? Hmm...this just needs to be called since I can't save the results within the markdown script...
# save_path = "C:/Users/zachm/Documents/George Mason/Projects/Labor Flows Paper/Results/Initial_results"


```


```{r load_dependencies, include = FALSE}

## Load libraries/functions
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)


## Load visualization functions
lpath = "C:/Users/zachm/Documents/George Mason/Projects/Labor Flows Paper/R visualizations"
source(paste(lpath, "fxns_firm.R", sep = "/"))
source(paste(lpath, "fxns_general.R", sep = "/"))
source(paste(lpath, "fxns_labor.R", sep = "/"))
source(paste(lpath, "fxns_network_smry.R", sep = "/"))

```


```{r local_fxns, include = FALSE}

## Note that we cannot create a SD here - we'd have to go back to the raw data and do so
## Do I really need the plots though? I can just look at the point estimates in equillibrium...

## A function to get self nominal or real wage ratio (by sector)
getPre2PostWageRatio = function(df,        # Data frame of interest (usually from getLocationData())
                                colname,   # Wage column of interest
                                new_name,  # What should the new column be called?
                                time_comp  # Time step to grab the wage comparison (should be last time before shock)
                                ){
  
  #### Input Checking ####
  
  
  #### Begin Function ####
  
  ## Note - can't divide standard deviations, so this is only calculated for the mean
  
  
  
  
  ## Get the ratio as new wage over the comp wage on a per location and per sector basis
  ## This gives as an appropriate looking gain/lost relative to the pre-shock equilibrium wage
  locs = unique(df$Mean$Name)
  sectors = unique(df$Mean$Sector)
  for (loc in locs){
    for (sector in sectors){
      
      idx = (df$Mean$Name == loc) & (df$Mean$Sector == sector)
      
      ## Get the vector of appropriate wages for the indices of interest
      tmp = df$Mean[[colname]][idx]
      comp_val = tmp[time_comp]
      
      tmp[1:time_comp] = 1
      id_shock = (time_comp + 1):length(tmp)
      tmp[id_shock] = comp_val / tmp[id_shock]
      
      df$Mean[idx, new_name] = tmp
    }
  }
  
  
  return(df)
}


## A function to get location nominal or real wage ratio (by sector)




```



#### Docked Comparison: `r docked_path`
#### WFH Comparison: `r wfh_path`

<br>

#### Last run: `r format(Sys.time(), "%b %d, %Y")` 


<p>

```{r print_description, include = TRUE, results = 'asis'}

cat(quick_description)

```

<p>



This script displays the results for a given model docked to Moretti's work and compares it to the appropriate WFH extension. 

Each graph presents the results stacked - Docked on top, WFH on the bottom. Note that because of the way these runs are conducted, the results display how WFH impacts the shock of the docked model.

```{r import_data, include = FALSE}

## Import docked data
df_firms_docked = getFirmData(paste(base_path, docked_path, sep = "/"))
df_loc_docked = getLocationData(paste(base_path, docked_path, sep = "/"))
loc_mean_docked = df_loc_docked$Mean
loc_sd_docked = df_loc_docked$Std



## Import WFH data
df_firms_wfh = getFirmData(paste(base_path, wfh_path, sep = "/"))
df_loc_wfh = getLocationData(paste(base_path, wfh_path, sep = "/"))
loc_mean_wfh = df_loc_wfh$Mean
loc_sd_wfh = df_loc_wfh$Std



```


### Firm Comparisons

```{r create_firm_plts, include = FALSE}

## Mean Workers Plot
plt1 = plotStatistic_location("Firm Mean Workers", loc_mean_docked, loc_sd_docked) + ylab("Docked")
plt2 = plotStatistic_location("Firm Mean Workers", loc_mean_wfh, loc_sd_wfh) + ylab("WFH")

ttl = ggdraw() + draw_label("Mean Workers per Firm", x = .15, size = 12) + theme_minimal()

plt_mean_workers = plot_grid(ttl,
                             plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                             ncol = 1, nrow = 2, rel_heights = c(.15, 1))


## Mean Profit Plot
plt1 = plotStatistic_location("Firm Mean Profit", loc_mean_docked, loc_sd_docked)
plt2 = plotStatistic_location("Firm Mean Profit", loc_mean_wfh, loc_sd_wfh)

ttl = ggdraw() + draw_label("Mean Profit per Firm", x = .15, size = 12) + theme_minimal()

plt_mean_profit = plot_grid(ttl,
                            plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                            ncol = 1, nrow = 2, rel_heights = c(.15, 1))


## Mean Unfulfilled Hiring Quota
plt1 = plotStatistic_location("Firm Mean Hiring Quota unfulfilled", loc_mean_docked, loc_sd_docked)
plt2 = plotStatistic_location("Firm Mean Hiring Quota unfulfilled", loc_mean_wfh, loc_sd_wfh)

ttl = ggdraw() + draw_label("Mean Unfulfilled Hiring Quota", x = .15, size = 12) + theme_minimal()

plt_hiring_quota = plot_grid(ttl,
                             plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                             ncol = 1, nrow = 2, rel_heights = c(.15, 1))


```


```{r print_firm_plts, include = TRUE, fig.height = 5, fig.width = 12}

plt_mean_workers
plt_mean_profit
plt_hiring_quota

```


### Location Comparisons - labor

```{r create_location_worker_plts, include = FALSE}

## Remote Workers
plt1 = plotStatistic_location("remote workers", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("remote workers", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Remote Workers", x = .15, size = 12) + theme_minimal()

plt_remote_workers = plot_grid(ttl,
                               plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                               ncol = 1, nrow = 2, rel_heights = c(.15, 1))


## This is includes unemployed...
## Mean Nominal Wage
plt1 = plotStatistic_location("mean wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("mean wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Nominal Wage", x = .15, size = 12) + theme_minimal()

plt_nom_wage_workers_wUnemp = plot_grid(ttl,
                                        plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                                        ncol = 1, nrow = 2, rel_heights = c(.15, 1))

## Mean Real Wage 
## Note - this should probably be plotted as a percent difference due to the rent calculation being crazy different with higher values of k
# loc_mean_docked$`Mean Real Wage wUnemp` = loc_mean_docked$`mean wage` / loc_mean_docked$rent
# loc_sd_docked$`Mean Real Wage wUnemp` = loc_sd_docked$`mean wage` / loc_sd_docked$rent
loc_mean_docked$`Mean Real Wage wUnemp` = loc_mean_docked$`mean real wage` 
loc_sd_docked$`Mean Real Wage wUnemp` = loc_sd_docked$`mean real wage`

# loc_mean_wfh$`Mean Real Wage wUnemp` = loc_mean_wfh$`mean wage` / loc_mean_wfh$rent
# loc_sd_wfh$`Mean Real Wage wUnemp` = loc_sd_wfh$`mean wage` / loc_sd_wfh$rent
loc_mean_wfh$`Mean Real Wage wUnemp` = loc_mean_wfh$`mean real wage` 
loc_sd_wfh$`Mean Real Wage wUnemp` = loc_sd_wfh$`mean real wage` 

ttl = ggdraw() + draw_label("Real Wage", x = .15, size = 12) + theme_minimal()

# plt1 = plotStatistic_location("Mean Real Wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
# plt2 = plotStatistic_location("Mean Real Wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("Docked")
plt1 = plotStatistic_location("Mean Real Wage wUnemp", loc_mean_docked, loc_sd_docked) + ggtitle("Docked") # Don't show the bands here because the SD really throws off the scale
plt2 = plotStatistic_location("Mean Real Wage wUnemp", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

plt_real_wage_workers_wUnemp = plot_grid(ttl,
                                         plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                                         ncol = 1, nrow = 2, rel_heights = c(.15, 1))



## This does not include unemployed
plt1 = plotStatistic_location("employed mean wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("employed mean wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Nominal Wage (excl unemployed)", x = .15, size = 12) + theme_minimal()

plt_nom_wage_workers = plot_grid(ttl,
                                 plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                                 ncol = 1, nrow = 2, rel_heights = c(.15, 1))

## Mean Real Wage 
## Note - this should probably be plotted as a percent difference due to the rent calculation being crazy different with higher values of k

loc_mean_docked$`Mean Real Wage` = loc_mean_docked$`employed mean real wage`
loc_sd_docked$`Mean Real Wage` = loc_sd_docked$`employed mean real wage`

loc_mean_wfh$`Mean Real Wage` = loc_mean_wfh$`employed mean real wage`
loc_sd_wfh$`Mean Real Wage` = loc_sd_wfh$`employed mean real wage` 


ttl = ggdraw() + draw_label("Real Wage (excl unemployed)", x = .15, size = 12) + theme_minimal()

# plt1 = plotStatistic_location("Mean Real Wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
# plt2 = plotStatistic_location("Mean Real Wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("Docked")
plt1 = plotStatistic_location("Mean Real Wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked") # Don't show the bands here because the SD really throws off the scale
plt2 = plotStatistic_location("Mean Real Wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

plt_real_wage_workers = plot_grid(ttl,
                                  plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                                  ncol = 1, nrow = 2, rel_heights = c(.15, 1))




## Rent
plt1 = plotStatistic_location("rent", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("rent", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Rent", x = .15, size = 12) + theme_minimal()

plt_rent = plot_grid(ttl,
                     plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                     ncol = 1, nrow = 2, rel_heights = c(.15, 1))




## Preferred Location 
plt1 = plotStatistic_location("preferred location", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("preferred location", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Preferred Location", x = .15, size = 12) + theme_minimal()

plt_pref_loc = plot_grid(ttl,
                         plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                         ncol = 1, nrow = 2, rel_heights = c(.15, 1))



## Proportion of workers in each location 
loc_mean_docked$`Proportion Workers` = loc_mean_docked$`N workers` / loc_mean_docked$`Total Workers Sector`
loc_mean_wfh$`Proportion Workers` = loc_mean_wfh$`N workers` / loc_mean_wfh$`Total Workers Sector`

plt1 = plotStatistic_location("Proportion Workers", loc_mean_docked, NULL) + ggtitle("Docked")
plt2 = plotStatistic_location("Proportion Workers", loc_mean_wfh, NULL) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Proportion Workers", x = .15, size = 12) + theme_minimal()

plt_N_prop = plot_grid(ttl,
                       plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                       ncol = 1, nrow = 2, rel_heights = c(.15, 1))

## Total Workers in each location (by Sector)
plt1 = plotStatistic_location("N workers", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("N workers", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("N Workers", x = .15, size = 12) + theme_minimal()



plt_N_tot = plot_grid(ttl,
                      plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                      ncol = 1, nrow = 2, rel_heights = c(.15, 1))




## Employment Rate
loc_mean_docked$`Employment Rate` = loc_mean_docked$`N Employed` / loc_mean_docked$`N workers`
loc_sd_docked$`Employment Rate` = loc_sd_docked$`N Employed` / loc_sd_docked$`N workers`

loc_mean_wfh$`Employment Rate` = loc_mean_wfh$`N Employed` / loc_mean_wfh$`N workers`
loc_sd_wfh$`Employment Rate` = loc_sd_wfh$`N Employed` / loc_sd_wfh$`N workers`


# plt1 = plotStatistic_location("Employment Rate", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
# plt2 = plotStatistic_location("Employment Rate", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")
plt1 = plotStatistic_location("Employment Rate", loc_mean_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("Employment Rate", loc_mean_wfh) + ggtitle("WFH")


ttl = ggdraw() + draw_label("Employment Rate", x = .15, size = 12) + theme_minimal()

plt_emp_rate = plot_grid(ttl,
                         plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                         ncol = 1, nrow = 2, rel_heights = c(.15, 1))






```

```{r print_location_worker_plts, include = TRUE, fig.height = 5, fig.width = 12}

plt_remote_workers
plt_nom_wage_workers
plt_real_wage_workers
plt_nom_wage_workers_wUnemp
plt_real_wage_workers_wUnemp
plt_rent
plt_pref_loc
plt_N_tot
plt_N_prop
plt_emp_rate

```

```{r calc_wage_ratio_eq, include=FALSE}

## Calculate the wage ratios and present them in a couple of tables:

## Self wage pre and post shock
n = length(unique(loc_mean_docked$Name)) * length(unique(loc_mean_docked$Sector)) # Note that this only works for 1 sector with 2 locations and 2 and 2 (need to remember how to do n choose k for more...)
self_real_wage_docked = rep(NA, n)
self_nominal_wage_docked = self_real_wage_docked
self_real_wage_wfh = self_real_wage_docked
self_nominal_wage_wfh = self_real_wage_docked
cnt = 1
cnames = rep(NA, n)
for (loc in unique(loc_mean_docked$Name)){
  for (sector in unique(loc_mean_docked$Sector)){
    
    idl = loc_mean_docked$Name == loc
    ids = loc_mean_docked$Sector == sector
    
    ## Including the unemployed
    tmp = loc_mean_docked$`mean real wage`[idl & ids]
    self_real_wage_docked[cnt] = tmp[600] / tmp[200]
    
    tmp = loc_mean_docked$`mean wage`[idl & ids]
    self_nominal_wage_docked[cnt] = tmp[600] / tmp[200]
    
    
    idl = loc_mean_wfh$Name == loc
    ids = loc_mean_wfh$Sector == sector
    
    tmp = loc_mean_wfh$`mean real wage`[idl & ids]
    self_real_wage_wfh[cnt] = tmp[600] / tmp[200]
    
    
    tmp = loc_mean_wfh$`mean wage`[idl & ids]
    self_nominal_wage_wfh[cnt] = tmp[600] / tmp[200]
    
    cnames[cnt] = paste0(loc, " - ", sector)
    cnt = cnt + 1
  }
}


self_real_wage_pre2post = matrix(data = c(self_real_wage_docked, self_real_wage_wfh), nrow = 2, ncol = n, byrow = TRUE)
colnames(self_real_wage_pre2post) = cnames
rownames(self_real_wage_pre2post) = c("Docked", "WFH")

self_nominal_wage_pre2post = matrix(data = c(self_nominal_wage_docked, self_nominal_wage_wfh), nrow = 2, ncol = n, byrow = TRUE)
colnames(self_nominal_wage_pre2post) = cnames
rownames(self_nominal_wage_pre2post) = c("Docked", "WFH")


## Kableize these tables for ease of viewing
tbl_wage_pre2post = kable(round(rbind(self_real_wage_pre2post, self_nominal_wage_pre2post), 2), 
                          row.names = TRUE, align = 'c',
                          caption = "Change in Wages pre-shock to post-shock") %>%
                      kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
                      pack_rows(group_label = "Real", start_row = 1, end_row = 2) %>%
                      pack_rows(group_label = "Nominal", start_row = 3, end_row = 4)



## Loc and Sector post shock
n = length(unique(loc_mean_docked$Sector))
comp_nominal_wage_docked = rep(NA, n)
comp_real_wage_docked = comp_nominal_wage_docked
comp_real_wage_wfh = comp_nominal_wage_docked
comp_nominal_wage_wfh = comp_nominal_wage_docked
cnt = 1
cnames = rep(NA, n)
for (sector in unique(loc_mean_docked$Sector)){
  
  cnames[cnt] = paste0("A/B - ", sector)
  
  idx = loc_mean_docked$Sector == sector
  idA = loc_mean_docked$Name == "Location A"
  idB = loc_mean_docked$Name == "Location B"
  idT = loc_mean_docked$`Time Step` == 600
  
  comp_nominal_wage_docked[cnt] = loc_mean_docked$`mean wage`[idx & idA & idT] / loc_mean_docked$`mean wage`[idx & idB & idT]
  comp_real_wage_docked[cnt] = loc_mean_docked$`mean real wage`[idx & idA & idT] / loc_mean_docked$`mean real wage`[idx & idB & idT]
  
  
  idx = loc_mean_wfh$Sector == sector
  idA = loc_mean_wfh$Name == "Location A"
  idB = loc_mean_wfh$Name == "Location B"
  idT = loc_mean_wfh$`Time Step` == 600
  
  comp_nominal_wage_wfh[cnt] = loc_mean_wfh$`mean wage`[idx & idA & idT] / loc_mean_wfh$`mean wage`[idx & idB & idT]
  comp_real_wage_wfh[cnt] = loc_mean_wfh$`mean real wage`[idx & idA & idT] / loc_mean_wfh$`mean real wage`[idx & idB & idT]
  
  cnt = cnt + 1
}

comp_real_wage_loc = matrix(data = c(comp_real_wage_docked, comp_real_wage_wfh), nrow = 2, ncol = n, byrow = TRUE)
colnames(comp_real_wage_loc) = cnames
rownames(comp_real_wage_loc) = c("Docked", "WFH")

comp_nominal_wage_loc= matrix(data = c(comp_nominal_wage_docked, comp_nominal_wage_wfh), nrow = 2, ncol = n, byrow = TRUE)
colnames(comp_nominal_wage_loc) = cnames
rownames(comp_nominal_wage_loc) = c("Docked", "WFH")

## Kableize these tables for ease of viewing
tbl_wage_loc_comp = kable(round(rbind(comp_real_wage_loc, comp_nominal_wage_loc), 2), 
                          row.names = TRUE, align = 'c',
                          caption = "Post-shock Wage Ratio by Location") %>%
                      kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
                      pack_rows(group_label = "Real", start_row = 1, end_row = 2) %>%
                      pack_rows(group_label = "Nominal", start_row = 3, end_row = 4)


## Loc and Sector post shock WFH and no WFH (may not actually need this)




```

The tables below compare wages pre- and post-shock within a sector, location, and model paradigm, as well as provide a ratio of final wages within each sector relative to Location B.

```{r print_wage_comp_tables, include = TRUE}

tbl_wage_pre2post

tbl_wage_loc_comp

```



### Location Comparisons - firm

```{r create_location_firm_plts, include = FALSE}

## Histograms of firm sizes (compare these side-by-side)
df_hist = do.call('rbind', df_firms_docked$Raw)
colnames(df_hist) = gsub("\\.", " ", colnames(df_hist))
df_hist = df_hist[df_hist$`Time Step` %in% c(0, 100, 199, 225, 245, 400),]
hist_docked = ggplot(df_hist, aes(x = `Total Workers`, fill = Location)) + 
                geom_histogram(bins = 45) +
                facet_grid(`Time Step` ~ Sector) +
                theme_minimal() +
                ggtitle("Firm Size - Docked")

df_hist = do.call('rbind', df_firms_wfh$Raw)
colnames(df_hist) = gsub("\\.", " ", colnames(df_hist))
df_hist = df_hist[df_hist$`Time Step` %in% c(0, 100, 199, 225, 245, 400),]
hist_wfh = ggplot(df_hist, aes(x = `Total Workers`, fill = Location)) + 
              geom_histogram(bins = 45) +
              facet_grid(`Time Step` ~ Sector) +
              theme_minimal() +
              ggtitle("Firm Size - WFH")


plt_hist = plot_grid(hist_docked, hist_wfh, ncol = 2, align = 'hv')




## This is only the Firm Wage average
plt1 = plotStatistic_location("Firm Mean Wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked")
plt2 = plotStatistic_location("Firm Mean Wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

ttl = ggdraw() + draw_label("Firm Mean Nominal Wage", x = .15, size = 12) + theme_minimal()

plt_nom_wage_firms = plot_grid(ttl,
                               plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                               ncol = 1, nrow = 2, rel_heights = c(.15, 1))

## Mean Real Wage 
## Note - this should probably be plotted as a percent difference due to the rent calculation being crazy different with higher values of k

loc_mean_docked$`Mean Real Wage` = loc_mean_docked$`Firm Mean Real Wage`
loc_sd_docked$`Mean Real Wage` = loc_sd_docked$`Firm Mean Real Wage`

# loc_mean_wfh$`Mean Real Wage` = loc_mean_wfh$`Firm Mean Wage` / loc_mean_wfh$rent
# loc_sd_wfh$`Mean Real Wage` = loc_sd_wfh$`Firm Mean Wage` / loc_sd_wfh$rent
loc_mean_wfh$`Mean Real Wage` = loc_mean_wfh$`Firm Mean Real Wage`
loc_sd_wfh$`Mean Real Wage` = loc_sd_wfh$`Firm Mean Real Wage` 


ttl = ggdraw() + draw_label("Firm Mean Real Wage", x = .15, size = 12) + theme_minimal()

plt1 = plotStatistic_location("Mean Real Wage", loc_mean_docked, loc_sd_docked) + ggtitle("Docked") # Don't show the bands here because the SD really throws off the scale
plt2 = plotStatistic_location("Mean Real Wage", loc_mean_wfh, loc_sd_wfh) + ggtitle("WFH")

plt_real_wage_firms = plot_grid(ttl,
                                plot_grid(plt1, plt2, rel_heights = c(1, 1), align = 'hv', ncol = 1, nrow = 2),
                                ncol = 1, nrow = 2, rel_heights = c(.15, 1))




```


```{r disp_loc_firm_plts, include = TRUE, fig.height=8, fig.width=12}

plt_hist

```

```{r disp_loc_firm_wage_plts, include = TRUE, fig.height = 5, fig.width = 12}

plt_nom_wage_firms
plt_real_wage_firms

```


### Network Comparisons 

```{r create_network_plts, include = FALSE}

net_df_docked = getNetworkSummaryData(paste(base_path, docked_path, sep = "/"))
net_df_wfh = getNetworkSummaryData(paste(base_path, wfh_path, sep = "/"))


plt_net_docked = cowplot::plot_grid(plotStatistic_networkSummary("Total Edges", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Total Edges"),
                                    plotStatistic_networkSummary("Global Clustering", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Global Clustering"),
                                    plotStatistic_networkSummary("Density", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Density"),
                                    ncol = 1, nrow = 3, align = 'hv')


plt_net_wfh = cowplot::plot_grid(plotStatistic_networkSummary("Total Edges", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Total Edges"),
                                 plotStatistic_networkSummary("Global Clustering", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Global Clustering"),
                                 plotStatistic_networkSummary("Density", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Density"),
                                 ncol = 1, nrow = 3, align = 'hv')

```


#### Docked: 

```{r plt_net_docked, include = TRUE, fig.height=6, fig.width=12}
plt_net_docked
```


#### WFH Comparison: 

```{r plt_net_wfh, include = TRUE, fig.height=6, fig.width=12}
plt_net_wfh
```


<!---
### Network by Location 

```{r create_network_plts_loc, include = FALSE}

net_df_docked = getNetworkSummaryData(paste(base_path, docked_path, sep = "/"))
net_df_wfh = getNetworkSummaryData(paste(base_path, wfh_path, sep = "/"))


plt_net_docked_loc = cowplot::plot_grid(plotStatistic_networkSummary("Total Edges", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Total Edges"),
                                    plotStatistic_networkSummary("Global Clustering", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Global Clustering"),
                                    plotStatistic_networkSummary("Density", net_df_docked$Mean, net_df_docked$Std) + ggtitle("Density"),
                                    ncol = 1, nrow = 3, align = 'hv')


plt_net_wfh_loc = cowplot::plot_grid(plotStatistic_networkSummary("Total Edges", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Total Edges"),
                                    plotStatistic_networkSummary("Global Clustering", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Global Clustering"),
                                    plotStatistic_networkSummary("Density", net_df_wfh$Mean, net_df_wfh$Std) + ggtitle("Density"),
                                    ncol = 1, nrow = 3, align = 'hv')

```


#### Docked: 

```{r plt_net_docked_loc, include = TRUE, fig.height=6, fig.width=12}
plt_net_docked_loc
```


#### WFH Comparison: 

```{r plt_net_wfh_loc, include = TRUE, fig.height=6, fig.width=12}
plt_net_wfh_loc
```

--->

## Firm Policy

*placeholder*

